How has the Brazilian Amazon been constructed as a problem:presidential speeches and transnational politics since 1985

### 2023-01-18 Submission/Re-submission/draft/draft_resubmission.rmd
added commented out codes to help with certain plot changes, if necessary

```{r Figure pure, fig.cap="Pure-types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
mmt1 <- ama_mx %>%
  filter(mx_cat2 == "Mixed-types") %>%
  count(mx_cat) %>%
  mutate(perc = n / sum(n)) # averages in relation to only mixed-types
mmt2 <- ama_mx %>%
  count(mx_cat)%>%
  mutate(perc = n / sum(n)) # averages in relation to full sample
ama_mx %>%
  count(mx_cat, mx_cat2, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(mx_cat2 == "Pure-types") %>%
  ggplot() +
  geom_smooth(aes(x=as.numeric(year), y = perc, color = mx_cat, fill = mx_cat),
              se = FALSE, linewidth =0.75, linetype="solid") +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "", y = "", title ="Share of each pure-type problem-construction by year",
       subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
       caption = "Curves in the plot were smoothed using loess method.") +
  theme_am() +
  facet_wrap("mx_cat") +
  geom_smooth(amazon_def_year, mapping = aes(x = year, y = def_year/100),
              color= "darkolivegreen", linetype="twodash", se = FALSE) +
  annotate("text", x = 2002, y = 0.14, label = "27772 km2\ndeforested" , size = 2)+
  annotate("text", x = 2013, y = 0.03, label = "4571 km2\ndeforested", size = 2)
```

>>>>

```{r Figure pure, fig.cap="Pure-types in time", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE}
mmt1 <- ama_mx %>%
  filter(mx_cat2 == "Mixed-types") %>%
  count(mx_cat) %>%
  mutate(perc = n / sum(n)) # averages in relation to only mixed-types
mmt2 <- ama_mx %>%
  count(mx_cat)%>%
  mutate(perc = n / sum(n)) # averages in relation to full sample
ama_mx %>%
  count(mx_cat, mx_cat2, year) %>%
  group_by(year) %>%
  mutate(perc = n / sum(n)) %>% 
  filter(mx_cat2 == "Pure-types") %>%
  ggplot() +
  geom_smooth(aes(x=as.numeric(year), y = perc, color = mx_cat, fill = mx_cat),
              se = FALSE, linewidth =0.75, linetype="solid") +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "", y = "", title ="Share of each pure-type problem-construction by year",
       subtitle = "Sample composed by 1924 Amazonian statements in presidential speeches since 1985",
       caption = "Curves in the plot were smoothed using loess method.") +
  theme_am() +
  # theme(legend.position = "bottom")+
  # guides(fill=guide_legend(nrow=2,byrow=TRUE)) +
  facet_wrap("mx_cat") +
  geom_smooth(amazon_def_year, mapping = aes(x = year, y = def_year/100),
              color= "darkolivegreen", linetype="twodash", se = FALSE) +
  annotate("text", x = 1989, y = 0.16, label = "Deforastation", size = 2) +
  annotate("text", x = 2001, y = 0.18, label = "27772 km2\ndeforested" , size = 2)+
  annotate("text", x = 2014, y = 0.03, label = "4571 km2\ndeforested", size = 2)
```
